Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs

### 2016-08-07 main_paper.tex
Edit the table of simulation results
Add simulation results for wild bootstrap and heteroskedastic data, with
uniform kernel.

Take down naive bootstrap and triagular kernel.

\begin{table}[t]
  \centering
  \begin{tabular}{rlrrrrrrr}
    \toprule
    DGP & Method     & Bias   & SD    & RMSE   & CI Coverage (\%) & CI Length \\
    \midrule
    1   & \bootuni   & --0.014 & 0.067 & 0.069 & 93.4       & 0.242     \\
        & \bootnaive & --0.040 & 0.042 & 0.058 & 89.0       & 0.182     \\
        & \cctuni    & --0.014 & 0.067 & 0.069 & 92.5       & 0.246     \\
        & \ccttri    & --0.011 & 0.067 & 0.068 & 91.4       & 0.239     \\
        & \naiveuni  & --0.040 & 0.042 & 0.058 & 81.5       & 0.156     \\\\
    2   & \bootuni   & --0.011 & 0.088 & 0.089 & 95.3       & 0.323     \\
        & \bootnaive & --0.151 & 0.067 & 0.165 & 35.4       & 0.269     \\
        & \cctuni    & --0.011 & 0.088 & 0.089 & 93.7       & 0.353     \\
        & \ccttri    & --0.008 & 0.086 & 0.086 & 93.2       & 0.346     \\
        & \naiveuni  & --0.151 & 0.067 & 0.165 & 29.5       & 0.230     \\\\
    3   & \bootuni   & --0.004 & 0.065 & 0.065 & 95.9       & 0.247     \\
        & \bootnaive &   0.033 & 0.052 & 0.062 & 91.3       & 0.215     \\
        & \cctuni    & --0.004 & 0.065 & 0.065 & 93.8       & 0.251     \\
        & \ccttri    & --0.005 & 0.065 & 0.065 & 93.4       & 0.244     \\
        & \naiveuni  &   0.033 & 0.052 & 0.062 & 86.1       & 0.191     \\
    \bottomrule
  \end{tabular}
  \caption{%
    Experimental coverage probabilities for each interval estimator based on 5000
    simulations; nominal coverage probabilities are 95\% for each estimator. The column
    ``CI Coverage'' lists the coverage frequency in these simulations and ``CI Length''
    lists the average length of the confidence interval across simulations.}
  \label{tbl:1}
\end{table}

>>>>

\begin{table}[t]
  \centering
  \begin{tabular}{rlrrrrrrr}
    \toprule
    DGP & Method       & Bias    & SD    & RMSE  & CI Coverage (\%) & CI Length \\
    \midrule                                                     \\
    \multicolumn{7}{l}{Homoskedastic data with $\gamma = 0$ (Panel A)}  \\
    \midrule
    1 & Wild bootstrap & --0.014 & 0.067 & 0.069 & 0.917 & 0.237 \\ 
      & CCT            & --0.014 & 0.067 & 0.069 & 0.924 & 0.246 \\ 
    2 & Wild bootstrap & --0.011 & 0.088 & 0.089 & 0.917 & 0.310 \\ 
      & CCT            & --0.011 & 0.088 & 0.089 & 0.935 & 0.351 \\
    3 & Wild bootstrap & --0.004 & 0.065 & 0.065 & 0.933 & 0.242 \\
      & CCT            & --0.004 & 0.065 & 0.065 & 0.938 & 0.251 \\ 
    \midrule                                                     \\
    \multicolumn{7}{l}{Heteroskedastic data with $\gamma = 2$ (Panel B)}  \\
    \midrule
    1 & Wild bootstrap & --0.011 & 0.081 & 0.081 & 0.924 & 0.289 \\
      & CCT            & --0.011 & 0.081 & 0.081 & 0.931 & 0.301 \\ 
    2 & Wild bootstrap & --0.011 & 0.097 & 0.098 & 0.912 & 0.334 \\ 
      & CCT            & --0.011 & 0.097 & 0.097 & 0.931 & 0.379 \\
    3 & Wild bootstrap &   0.000 & 0.116 & 0.116 & 0.923 & 0.409 \\ 
      & CCT            &   0.000 & 0.116 & 0.116 & 0.935 & 0.432 \\
    \bottomrule
  \end{tabular}
  \caption{%
    Experimental coverage probabilities for each interval estimator based on 5000
    simulations; nominal coverage probabilities are 95\% for each estimator. The column
    ``CI Coverage'' lists the coverage frequency in these simulations and ``CI Length''
    lists the average length of the confidence interval across simulations.}
  \label{tbl:1}
\end{table}
